---
title: "Class Action Survey - Document export"
author: "Adi Sarid / Sarid Research Institute / adi@sarid-ins.co.il"
date: "1/30/2019"
output: 
  html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Data collection

The data was collected online:

   * General public's survey via online panel (representative of the Hebrew speaking general public in Israel)
   * Lawyers using contact lists (conference participants and additional subscribers of knowit.org.il)

## Load files

Files are stored in subdir /data of the repo. We read the xlsx files to avoid messing with any encoding problems. The files are relatively small.
```{r read files}
library(tidyverse)

# public opionion dataset
public <- readxl::read_excel("../data/export-9524846-general_public.xlsx")
public_conjoint <- readxl::read_excel("../data/export-9524846-general_public-conjoint.xlsx")

glimpse(public)
glimpse(public_conjoint)

# attorney dataset
attorney <- readxl::read_excel("../data/export-9524911-attorneys.xlsx")

glimpse(attorney)


```

## General public's awareness and knowledge

We started by asking the respondents if the ever hear the term class action (yes/no), and if they did - what sentence best describes what a class action is (multiple response).

```{r awareness and knowledge}
# auxiliary function for proportions
prop <- function(data, count_var = n, na.rm = T, sort_res = T){
  count_var <- enquo(count_var)
  if (na.rm) {
    res <- data %>% 
      count(!! count_var) %>% 
      filter(!is.na(!! count_var)) %>% 
      mutate(prop = n/sum(n))
  } else {
    res <- data %>% 
      count(!! count_var) %>% 
      mutate(prop = n/sum(n))
  }
  
  if (sort_res){
    res <- res %>% 
      arrange(desc(prop))
  }
  
  return(res)
  
}
  
public %>% 
  prop(q1_hear_term_class_action)

public_knowledge <- public %>%
  mutate(q2_what_is_modified = ifelse(q1_hear_term_class_action == 0,
                                      "dont_know",
                                      q2_what_is_a_class_action)) %>% 
  prop(q2_what_is_modified) %>% 
  mutate(class_action = 
           recode_factor(q2_what_is_modified,
                         public_suit_individual_loss = "תביעה של ציבור שלכל פרט שבו נגרם נזק קטן",
                         advance_public_rights = "כלי שמאפשר קידום זכויות לציבור הרחב",
                         state_neglect = "תביעה במקרים שהמדינה לא מטפלת בעוולות והפרות של חברות",
                         lawyer_get_rich = "כלי להתעשרות של עורכי דין",
                         dont_know = "לא יודע/ת",
                         other_specify = "אחר"
                         )) %>% 
  select(class_action, prop, n)
DT::datatable(public_knowledge)

ggplot_factor <- function(data, 
                          xvar,
                          xlabel = "", 
                          ylabel = "שיעור המשיבים",
                          gtitle = "",
                          colfill = "lightblue",
                          xsize = 14,
                          wrap_width = 15) {
  data <- data %>% 
    mutate(xfactor = fct_inorder(str_wrap(!! enquo(xvar), width = wrap_width) %>% 
                                   str_replace_all(., fixed("\n"), "\n\u202B")))
  
  output_plot <- ggplot(data, aes(x = xfactor, y = prop)) +
    geom_col(fill = "lightblue", color = "black") +
    geom_label(aes(label = paste0(round(prop*100), "%"))) + 
    scale_y_continuous(labels = scales::percent_format(accuracy = 1)) + 
    xlab(paste0("\u202B",xlabel)) + 
    ylab(paste0("\u202B",ylabel)) + 
    ggtitle(paste0("\u202B", gtitle)) + 
    theme(plot.title = element_text(hjust = 1), 
          panel.grid = element_line(color = "gray75"),
          axis.text.x = element_text(size = xsize),
          panel.background = element_rect(fill = NA),
          panel.border = element_rect(fill = NA, color = "gray75"))
  
  if ("n" %in% names(data)){
    output_plot <- output_plot + 
      labs(caption = paste0("n=", sum(data$n)))
  }
  
  return(output_plot)
  
  }

public_knowledge_chart <- ggplot_factor(public_knowledge, xvar = class_action,
              gtitle = "מהי תובענה ייצוגית בעיני הציבור?\nשאלה נעזרת")

public_knowledge_chart

# ggsave("figures/public_knowledge.png", public_knowledge_chart, width = 25, height = 10, units = "cm")

```

## Compensation in the last five years

We asked the general public: "To the best of your knowledge, in the last 5 years, did you receive any compensation as a results of a class action?"

```{r compensation five years}
compensation_received_chart <- public %>% 
  prop(q6_receive_benefit) %>% 
  filter(q6_receive_benefit %in% c(0, 1, -99)) %>% 
  mutate(q6_receive_recoded = 
           recode_factor(q6_receive_benefit,
                         `0` = "לא קיבלתי",
                         `1` = "קיבלתי",
                         `-99` = "לא זוכר")) %>% 
  ggplot_factor(q6_receive_recoded, gtitle = "האם קיבלת פיצוי?")

compensation_received_chart

# ggsave("figures/compensation_received_chart.png", compensation_received_chart, width = 20, height = 10, units = "cm")

compensation_what <- public %>% 
  prop(q8_receive_how) %>% 
  filter(q8_receive_how %in% c("cash", "benefit_discount", "cheque", "coupon")) %>% 
  mutate(q8_recoded = recode_factor(q8_receive_how,
                                    cash = "מזומן",
                                    benefit_discount = "הטבה / הנחה ברכישה",
                                    cheque = "צ'ק",
                                    coupon = "קופון")) %>% 
  ggplot_factor(q8_recoded, gtitle = "באיזה אופן התקבל הפיצוי?")

# ggsave("figures/compensation_what.png", compensation_what, width = 25, height = 10, units = "cm")

```

## To what extent do class actions help defend public rights?

This is a question which was presented both to the general public and lawyers. The answers were given on a 1-5 scale (1 = not at all,..., 5 = to a great extent).

```{r class defend public}

defend_public <- public %>% 
  filter(q5_class_action_defend_public %in% 1:5) %>% 
  prop(q5_class_action_defend_public) %>% 
  mutate(pop = "ציבור כללי") %>% 
  rename(ranking = q5_class_action_defend_public) %>%
  mutate(ranking = as.numeric(ranking)) %>% 
  bind_rows(attorney %>% 
              prop(`q8_defend_public:q_item_`) %>% 
              mutate(pop = "עורכי דין") %>% 
              rename(ranking = `q8_defend_public:q_item_`)) %>% 
  mutate(ranking_factor = 
           recode_factor(ranking,
                         `1` = "כלל לא",
                         `2` = "במידה מועטה",
                         `3` = "במידה בינונית",
                         `4` = "במידה רבה",
                         `5` = "במידה רבה מאוד"))

defend_public %>% 
  group_by(pop) %>% 
  summarize(tot_sample_size = sum(n),
            avg_rank = sum(ranking*prop))

defend_public_chart <- ggplot(defend_public, aes(x = ranking, y = prop, fill = ranking_factor)) +
  geom_bar(stat = "identity", position = "dodge", color = "black") +
  geom_label(aes(label = paste0(round(prop*100), "%")),position = position_dodge(width = 1),
             show.legend = F) + 
  guides(fill = guide_legend("דירוג")) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) + 
  xlab(paste0("\u202B","אוכלוסיה")) + 
  ylab(paste0("\u202B","שיעור המשיבים %")) + 
  ggtitle(paste0("\u202B", "באיזו מידה תובענות ייצוגיות עוזרות להגן על זכויות הציבור?")) + 
  theme(plot.title = element_text(hjust = 1), 
        panel.grid = element_line(color = "gray75"),
        axis.text.x = element_text(size = 13),
        strip.text = element_text(size = 13),
        panel.background = element_rect(fill = NA),
        panel.border = element_rect(fill = NA, color = "gray75")) + 
  facet_wrap(~ pop) +
  scale_fill_brewer(type = "div", palette = "RdYlGn") + 
  labs(caption = "\u202Bגודל מדגם: 181 עורכי דין, 482 משיבים מקרב הציבור הכללי")
  
# ggsave("figures/defend_public_chart.png", defend_public_chart, width = 25, height = 10, units = "cm")

```

Now, we split that same analysis only this time differentiate between prosecutors to defense.

```{r defend public split prosecutors defense}
attorney %>% 
  select(starts_with("q18_"), starts_with("q8_")) %>% 
  filter(q18_representation %in% c("defendents", "prosecutors")) %>% 
  group_by(q18_representation) %>% 
  summarize(mean = mean(`q8_defend_public:q_item_`))

defend_public_representation_split <- attorney %>% 
  select(starts_with("q18_"), starts_with("q8_")) %>% 
  filter(q18_representation %in% c("defendents", "prosecutors")) %>% 
  group_by(q18_representation) %>% 
  prop(`q8_defend_public:q_item_`) %>% 
  mutate(ranking = factor(`q8_defend_public:q_item_`,
                          levels = 1:5)) %>% 
  rename(pop = q18_representation) %>% 
  mutate(ranking_factor = 
           recode_factor(ranking,
                         `1` = "כלל לא",
                         `2` = "במידה מועטה",
                         `3` = "במידה בינונית",
                         `4` = "במידה רבה",
                         `5` = "במידה רבה מאוד")) %>% 
  ungroup() %>% 
  mutate(pop = recode_factor(pop,
                             prosecutors = "מייצג תובעים",
                             defendents = "מייצג נתבעות"))
  
attorney %>% count(q18_representation)


defend_law_side_chart <- ggplot(defend_public_representation_split, aes(x = ranking, y = prop, fill = ranking_factor)) +
  geom_bar(stat = "identity", position = "dodge", color = "black") +
  geom_label(aes(label = paste0(round(prop*100), "%")),position = position_dodge(width = 1),
             show.legend = F) + 
  guides(fill = guide_legend("דירוג")) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) + 
  xlab(paste0("\u202B","אוכלוסיה")) + 
  ylab(paste0("\u202B","שיעור המשיבים %")) + 
  ggtitle(paste0("\u202B", "באיזו מידה תובענות ייצוגיות עוזרות להגן על זכויות הציבור?")) + 
  theme(plot.title = element_text(hjust = 1), 
        panel.grid = element_line(color = "gray75"),
        axis.text.x = element_text(size = 13),
        strip.text = element_text(size = 13),
        panel.background = element_rect(fill = NA),
        panel.border = element_rect(fill = NA, color = "gray75")) + 
  facet_wrap(~ pop) +
  scale_fill_brewer(type = "div", palette = "RdYlGn") + 
  labs(caption = "\u202Bגודל מדגם: 53 מייצגים נתבעות, 63 מייצגים תובעים. היתר סירבו להשיב או מייצגים את שני הצדדים.")

# ggsave("figures/defend_law_side_chart.png", defend_law_side_chart, width = 25, height = 10, units = "cm")

aov(data = attorney,
    formula = `q8_defend_public:q_item_` ~ q18_representation) %>% 
  summary()

wilcox.test(formula = `q8_defend_public:q_item_` ~ q18_representation,
            data = attorney %>% 
              select(starts_with("q18_"), starts_with("q8_")) %>% 
              filter(q18_representation %in% c("defendents", "prosecutors")))

attorney %>% 
  select(starts_with("q18_"), starts_with("q8_")) %>%
  filter(q18_representation %in% c("defendents", "prosecutors")) %>% 
  group_by(q18_representation) %>% 
  summarize(mean = mean(`q8_defend_public:q_item_`))
  
```

## Compensation - conjoint analysis

```{r conjoint analysis public}
glm_set <- public_conjoint %>% 
  mutate(score_selection = score_selection/100) %>% 
  mutate(compensation_push_pull = factor(compensation_push_pull,
                                         levels = c("pull", "push"),
                                         ordered = F),
         compensation_type = factor(compensation_type,
                                    levels = 
                                      c("another_product",
                                        "refund_next_purchase",
                                        "coupon",
                                        "bank_cheque",
                                        "credit_cart"),
                                    ordered = F)) %>% 
  left_join(public %>% 
              select(`Response ID`, gender, age, income, family_status, edu, employment)) %>% 
  select(-`Set Number`, -`Card Number`, -`Response ID`) %>% 
  mutate(compensation_amount_ILS = factor(compensation_amount_ILS, levels = c(25, 50, 75, 100)))

glm(data = glm_set, 
    formula = score_selection ~ .) %>% summary()
```

It seems that the demographic variables do not add much to the analysis, and it is easier to work with the compensation variables.

```{r conjoint clean}
conjoint_glm_model <- glm(data = glm_set %>% 
      select(score_selection, compensation_push_pull, compensation_amount_ILS, compensation_type),
    formula = score_selection ~ .,
    family = binomial())
summary(conjoint_glm_model)

exp(coef(conjoint_glm_model))
```

We can also compute the odds ratio by using coefficients.

```{r conjoint logistic model coefficients}
exp(coef(conjoint_glm_model))

model_effect_plot <- jtools::plot_summs(conjoint_glm_model, scale = TRUE, inner_ci_level = 0.95, exp = T) + 
  ggtitle("העדפות בנוגע לאופן קבלת הפיצוי בתביעה ייצוגית") + 
  theme(plot.title = element_text(hjust = 1)) + 
  xlab("\u202Bפי כמה עולה הסיכוי לבחירה באפשרות זו?")

model_effect_plot

# ggsave("figures/model_effect_plot.png", model_effect_plot, width = 20, height = 10, units = "cm")

```

## Class action submission fees

One of Ayelet Shaked's moves was to establish a class action submission fee of 16k ILS, in order to reduce the number of class actions and reduce the overhead on the judicial system. We asked whether this step is positive or negative.

```{r submission fees}
public %>% 
  filter(q9_support_increased_fee %in% 1:5) %>% 
  prop(q9_support_increased_fee) %>% 
  arrange(q9_support_increased_fee) %>%
  mutate(q9_support_increased_fee = 
           recode_factor(q9_support_increased_fee,
                         `1` = "מתנגד במידה רבה",
                         `2` = "מתנגד",
                         `3` = "לא תומך ולא מתנגד",
                         `4` = "תומך",
                         `5` = "תומך במידה רבה")) %>% 
  ggplot_factor(xvar = q9_support_increased_fee, 
                gtitle = str_wrap(
                  "באחרונה יזמה שרת המשפטים תקנה שאושרה בכנסת המגדילה את אגרת ההגשה... מטרת המהלך היתה למנוע תביעות סרק ולצמצם את העומס... באיזו מידה אתה תומך או מתנגד למהלך זה?",
                  width = 70
                ) %>% 
                  str_replace_all(., "\n", "\n\u202B")) -> updated_fee_regulations

# ggsave("figures/updated_fee_regulations.png", updated_fee_regulations, width = 20, height = 10, units = "cm")

public %>% 
  prop(q15_fee_prevent_filing) %>% 
  mutate(q15_fee_prevent_filing = recode_factor(q15_fee_prevent_filing,
                                                `1` = "כן",
                                                `0` = "לא",
                                                `-99` = "לא יודע")) %>% 
  ggplot(aes(x = q15_fee_prevent_filing, y = prop, fill = q15_fee_prevent_filing)) +
    geom_col(color = "black") +
    geom_label(aes(label = paste0(round(prop*100), "%")), show.legend = F) + 
    scale_y_continuous(labels = scales::percent_format(accuracy = 1)) + 
    ylab(paste0("\u202B","שיעור המשיבים")) + 
    xlab("") +
    ggtitle(paste0("\u202B", 
                   str_wrap("כפי שנאמר בשאלה הקודמת, סכום האגרה בבית משפט מחוזי הוא 16,000 שח. האם סכום זה ימנע ממך להגיש תביעה יצוגית?",
                            width = 65) %>% 
                     str_replace_all(.,"\n", "\n\u202B"))) + 
    theme(plot.title = element_text(hjust = 1), 
          panel.grid = element_line(color = "gray75"),
          axis.text.x = element_text(size = 13),
          panel.background = element_rect(fill = NA),
          panel.border = element_rect(fill = NA, color = "gray75")) +
    guides(fill = F) -> prevent_filing_chart

# ggsave("figures/prevent_filing_chart.png", prevent_filing_chart, width = 20, height = 10, units = "cm")

```

## Fields for future lawsuits

In what fields did you consider or are currently considering to file for a class action?

```{r future class action fields}
public %>% 
  prop(q13_considering_filing) %>% 
  filter(q13_considering_filing%in% 0:1)

public %>%
  select(`Response ID`, contains("q14"), -contains("specify")) %>% 
  gather(lawsuit_field, selection, -`Response ID`) %>% 
  filter(!is.na(selection)) %>% 
  filter(selection != 0) %>% 
  count(lawsuit_field) %>% 
  mutate(prop = n/45) %>% 
  mutate(lawsuit_field = str_replace(lawsuit_field, ":q14_filing_field", ""))

```

## Leading offices in class action quality

Who are the leading law offices in class action lawsuit quality? representation quality?

### Lawsuit quality

```{r leading law offices}
attorney %>% 
  select(contains("q9"), `Response ID`,
         -contains("אחר")) %>% 
  gather(name, votes, -`Response ID`) %>% 
  mutate(votes = (!is.na(votes))*1) %>% 
  group_by(`Response ID`) %>% 
  summarize(total_votes = sum(votes)) %>% 
  filter(total_votes > 0) %>% 
  select(-total_votes) %>% 
  unique() %>% 
  NROW() -> total_respondents

prosecutor_rank <- attorney %>% 
  select(contains("q9"), `Response ID`,
         -contains("אחר")) %>% 
  gather(name, votes, -`Response ID`) %>% 
  mutate(votes = (!is.na(votes))*1) %>%
  filter(votes > 0) %>% 
  mutate(name = ifelse(str_detect(name, "חן שטיין"), 
                       "חן שטיין",
                       name)) %>% 
  prop(name) %>% 
  select(-prop) %>% 
  mutate(prop = n/total_respondents) %>% 
  mutate(name = str_replace(name, ":q9_prosecutors", "")) %>% 
  mutate(name = fct_inorder(name))

ggplot_factor(prosecutor_rank, name, wrap_width = 15) + 
  theme(axis.text.x = element_text(angle = 90, size = 10),
        panel.background = element_rect(fill = NA),
        panel.border = element_rect(fill = NA, color = "gray75")) +
  labs(caption = paste0("n=", total_respondents)) -> all_prosecutors_chart

# ggsave("figures/all_prosecutors_chart.png", all_prosecutors_chart, width = 30, height = 10, units = "cm")

#top10

ggplot_factor(prosecutor_rank %>% head(10), name, wrap_width = 15) + 
  theme(axis.text.x = element_text(angle = 0, size = 10),
        panel.background = element_rect(fill = NA),
        panel.border = element_rect(fill = NA, color = "gray75")) +
  labs(caption = paste0("n=", total_respondents)) -> top10_prosecutors_chart

# ggsave("figures/top10_prosecutors_chart.png", top10_prosecutors_chart, width = 30, height = 10, units = "cm")  

```

### Representation quality

```{r leading law offices}
attorney %>% 
  select(contains("q10"), `Response ID`,
         -contains("אחר")) %>% 
  gather(name, votes, -`Response ID`) %>% 
  mutate(votes = (!is.na(votes))*1) %>% 
  group_by(`Response ID`) %>% 
  summarize(total_votes = sum(votes)) %>% 
  filter(total_votes > 0) %>% 
  select(-total_votes) %>% 
  unique() %>% 
  NROW() -> total_respondents

defendents_rank <- attorney %>% 
  select(contains("q10"), `Response ID`,
         -contains("אחר")) %>% 
  gather(name, votes, -`Response ID`) %>% 
  mutate(votes = (!is.na(votes))*1) %>%
  filter(votes > 0) %>%  
  prop(name) %>% 
  select(-prop) %>% 
  mutate(prop = n/total_respondents) %>% 
  mutate(name = str_replace(name, ":q10_defendant", "")) %>% 
  mutate(name = fct_inorder(name))

ggplot_factor(defendents_rank, name, wrap_width = 30) + 
  theme(axis.text.x = element_text(angle = 90, size = 10),
        panel.background = element_rect(fill = NA),
        panel.border = element_rect(fill = NA, color = "gray75")) +
  labs(caption = paste0("n=", total_respondents)) -> all_defendents_chart

# ggsave("figures/all_defendents_chart.png", all_defendents_chart, width = 30, height = 10, units = "cm")

#top10

ggplot_factor(defendents_rank %>% head(10), name, wrap_width = 15) + 
  theme(axis.text.x = element_text(angle = 0, size = 10),
        panel.background = element_rect(fill = NA),
        panel.border = element_rect(fill = NA, color = "gray75")) +
  labs(caption = paste0("n=", total_respondents)) -> top10_defendents_chart

# ggsave("figures/top10_defendents_chart.png", top10_defendents_chart, width = 30, height = 10, units = "cm")  

```

## The judges most supportive or against class action lawsuits

```{r judge rank}
# all respondents
judge_rank_all <- attorney %>% 
  select(q11_judge_support, q12_judge_opposed) %>% 
  gather(type, selection) %>% 
  filter(!is.na(selection)) %>% 
  count(type, selection) %>% 
  group_by(type) %>% 
  mutate(prop = n/sum(n)) %>% 
  mutate(representation = "all") %>% 
  ungroup() %>% 
  mutate(type = recode_factor(type,
                              q12_judge_opposed = "מתנגד/ת לתובענות",
                              q11_judge_support = "אוהד/ת תובענות")) %>% 
  arrange(type, desc(prop)) %>% 
  mutate(selection = fct_inorder(selection))
  
# split to prosecutors/defendents
judge_rank_side_split <- attorney %>% 
  select(q11_judge_support, q12_judge_opposed, q18_representation) %>% 
  gather(type, selection, -q18_representation) %>% 
  filter(!is.na(selection)) %>% 
  filter(q18_representation %in% c("prosecutors", "defendents")) %>% 
  count(type, selection, q18_representation) %>% 
  group_by(type, q18_representation) %>% 
  mutate(prop = n/sum(n)) %>% 
  rename(representation = q18_representation) %>%
  ungroup() %>% 
  mutate(type = recode_factor(type,
                              q12_judge_opposed = "מתנגד/ת לתובענות",
                              q11_judge_support = "אוהד/ת תובענות")) %>% 
  mutate(representation = recode_factor(representation,
                                        prosecutors = "מייצגים תובעים",
                                        defendents = "מייצגים נתבעות")) %>% 
  mutate(selection = factor(selection,
                       levels = levels(judge_rank_all$selection)))

judge_rank_all %>% group_by(type) %>% summarize(sum(n))

ggplot(judge_rank_all, aes(fill = type, x = selection, y = prop)) +
  geom_col(color = "black", position = "dodge") + 
  geom_label(aes(label = paste0(round(prop*100), "%")), show.legend = F, position = position_dodge(width = .9), size = 2.5) + 
  guides(fill = guide_legend("סיווג השופט/ת", title.position = "top", title.hjust = 1)) + 
  theme(plot.title = element_text(hjust = 1), legend.position = "bottom",
        panel.grid = element_line(color = "gray75"),
        axis.text.x = element_text(size = 12, angle = 70, hjust = 1),
        panel.background = element_rect(fill = NA),
        panel.border = element_rect(fill = NA, color = "gray75")) + 
  ggtitle("השופט/ת האוהד/ת ביותר והשופט/ת המתנגד/ת ביותר") +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) + 
  ylab("\u202Bשיעור המשיבים %") + 
  xlab("") + 
  labs(caption = "n=146-148") -> judge_rank_all_chart
  
  

# ggsave("figures/judge_rank_all_chart.png", judge_rank_all_chart, width = 32, height = 12, units = "cm")

ggplot(judge_rank_side_split, aes(fill = type, x = selection, y = prop)) +
  geom_col(color = "black", position = "dodge") + 
  geom_label(aes(label = paste0(round(prop*100), "%")), show.legend = F, position = position_dodge(width = .9), size = 2) + 
  guides(fill = guide_legend("סיווג השופט/ת", title.position = "top", title.hjust = 1)) + 
  theme(plot.title = element_text(hjust = 1), legend.position = "bottom",
        panel.grid = element_line(color = "gray75"),
        axis.text.x = element_text(size = 12, angle = 70, hjust = 1),
        panel.background = element_rect(fill = NA),
        panel.border = element_rect(fill = NA, color = "gray75")) + 
  ggtitle("השופט/ת האוהד/ת ביותר והשופט/ת המתנגד/ת ביותר") +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) + 
  ylab("\u202Bשיעור המשיבים %") + 
  xlab("") + 
  labs(caption = "n=53-63") +
  facet_grid(rows = vars(representation)) -> judge_rank_split_chart
  
# ggsave("figures/judge_rank_split_chart.png", judge_rank_split_chart, width = 32, height = 12, units = "cm")
```

## The district court most favorable for class actions

```{r district court}
attorney %>% 
  prop(q14_court) %>% 
  ggplot_factor(q14_court, gtitle = "איזה בית משפט מחוזי לדעתך, הכי אוהד תובענות ייצוגיות?") -> most_pro_court_chart

# ggsave("figures/most_pro_court_chart.png", most_pro_court_chart, width = 30, height = 10, units = "cm")

attorney %>% 
  group_by(q18_representation) %>% 
  prop(q14_court) %>% 
  filter(q18_representation %in% c("prosecutors", "defendents"))
```

## Most profitable fields to issue a class action

```{r most profitable fields}
total_sample <- attorney %>% 
  select(contains("q15_subject_profit"), `Response ID`) %>% 
  gather(item, selection, -`Response ID`) %>% 
  filter(!is.na(selection)) %>% 
  select(`Response ID`) %>% 
  unique() %>% 
  NROW()

profitable_fields_chart <- attorney %>% 
  select(contains("q15_subject_profit")) %>% 
  gather(item, selection) %>% 
  filter(!is.na(selection)) %>% 
  count(item) %>% 
  mutate(prop = n/total_sample) %>% 
  mutate(item = str_replace(item, ":q15_subject_profit", "")) %>% 
  arrange(desc(prop)) %>% 
  ggplot_factor(item) + 
  labs(caption = paste0("n=", total_sample)) +
  theme(axis.text.x = element_text(angle = 65, hjust = 1))

# ggsave("figures/profitable_fields_chart.png", profitable_fields_chart, width = 30, height = 10, units = "cm")

```

### Most profitable fields to work a class action case - split by type of representation

```{r most profitable fields split}
total_sample <- attorney %>% 
  select(contains("q15_subject_profit"), `Response ID`, q18_representation) %>% 
  gather(item, selection, -q18_representation, -`Response ID`) %>% 
  filter(!is.na(selection)) %>% 
  count(`Response ID`, q18_representation) %>%
  filter(q18_representation %in% c("prosecutors", "defendents")) %>%
  select(1:2) %>% 
  unique() %>% 
  count(q18_representation) %>% 
  rename(sample_size = n)

profitable_fields_split_chart <- attorney %>% 
  select(contains("q15_subject_profit"), q18_representation) %>% 
  gather(item, selection, -q18_representation) %>% 
  filter(!is.na(selection)) %>% 
  count(item, q18_representation) %>% 
  filter(q18_representation %in% c("prosecutors", "defendents")) %>% 
  left_join(total_sample) %>% 
  mutate(prop = n/sample_size) %>% 
  mutate(item = str_replace(item, ":q15_subject_profit", "")) %>% 
  arrange(q18_representation, desc(prop)) %>% 
  mutate(item = fct_inorder(str_wrap(item, width = 20))) %>% 
  mutate(q18_representation = recode_factor(q18_representation,
                                            prosecutors = "מייצג תובעים",
                                            defendents = "מייצג נתבעים")) %>% 
  ggplot(aes(fill = q18_representation, x = item, y = prop)) +
  geom_col(color = "black", position = "dodge") + 
  geom_label(aes(label = paste0(round(prop*100), "%")), show.legend = F, position = position_dodge(width = .9), size = 2) + 
  guides(fill = guide_legend("סיווג התחום", title.position = "top", title.hjust = 1)) + 
  theme(plot.title = element_text(hjust = 1), legend.position = "bottom",
        panel.grid = element_line(color = "gray75"),
        axis.text.x = element_text(size = 12, angle = 70, hjust = 1),
        panel.background = element_rect(fill = NA),
        panel.border = element_rect(fill = NA, color = "gray75")) + 
  ggtitle("תחומי התביעות שבהם שכר הטרחה הכי משתלם - פילוח לפי צד") +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) + 
  ylab("\u202Bשיעור המשיבים %") + 
  xlab("") + 
  labs(caption = "n=53-63. total percent > 100% because more than one selection was possible")  

# ggsave("figures/profitable_fields_split_chart.png", profitable_fields_split_chart, width = 30, height = 13, units = "cm")
```

## Positions about class actions (1-5 likert scale questions)

```{r positions}

likert_scale_recoded <- attorney %>% 
  select(ends_with(":q_item_"), q2_new_regulations, q18_representation) %>% 
  gather(item, ranking, -q18_representation) %>% 
  mutate(item = str_replace(item, fixed(":q_item_"), "")) %>% 
  mutate(item = recode(item,
                       q2_new_regulations = "צמצום אפשרויות התביעה - התפתחות חיובית",
                       q3_supreme_court_pro_class = "העליון אוהד ייצוגיות", 
                       q4_legal_fees = "שכ''ט משקף את המאמץ",
                       q5_file_dismissal_legal_fees = "בהסתלקויות יש הצדקה לשכ''ט וגמול",
                       q6_class_amount = "כמות התובענות ראוייה",
                       q7_attorney_general_position = "עמדות היועמ''ש בתובענות ייצוגיות חשובות",
                       q8_defend_public = "ייצוגיות - הגנה על זכויות הציבור") %>% 
           str_wrap(width = 18) %>% 
           str_replace_all("\n", "\n\u202B")) %>% 
  filter(!is.na(ranking))

sort_order <- attorney %>% 
  select(ends_with(":q_item_"), q2_new_regulations) %>% 
  gather(item, ranking) %>% 
  mutate(item = str_replace(item, fixed(":q_item_"), "")) %>% 
  mutate(item = recode(item,
                       q2_new_regulations = "צמצום אפשרויות התביעה - התפתחות חיובית",
                       q3_supreme_court_pro_class = "העליון אוהד ייצוגיות", 
                       q4_legal_fees = "שכ''ט משקף את המאמץ",
                       q5_file_dismissal_legal_fees = "בהסתלקויות יש הצדקה לשכ''ט וגמול",
                       q6_class_amount = "כמות התובענות ראוייה",
                       q7_attorney_general_position = "עמדות היועמ''ש בתובענות ייצוגיות חשובות",
                       q8_defend_public = "ייצוגיות - הגנה על זכויות הציבור") %>% 
           str_wrap(width = 18) %>% 
           str_replace_all("\n", "\n\u202B")) %>% 
  filter(!is.na(ranking)) %>% 
  group_by(item) %>% 
  summarize(mean = mean(ranking)) %>% 
  arrange(desc(mean))
  
  

likert_scale_recoded_all <- likert_scale_recoded %>% 
  select(-q18_representation) %>% 
  group_by(item) %>% 
  prop(ranking) %>% 
  mutate(ranking_factor = 
           recode_factor(ranking,
                         `1` = "כלל לא",
                         `2` = "במידה מועטה",
                         `3` = "במידה בינונית",
                         `4` = "במידה רבה",
                         `5` = "במידה רבה מאוד")) %>% 
  ungroup() %>% 
  mutate(item = factor(item, levels = sort_order$item))

likert_scale_recoded_all_chart <- ggplot(likert_scale_recoded_all, aes(x = item, y = prop, fill = ranking_factor)) +
  geom_bar(stat = "identity", position = "fill", color = "black") +
  geom_label(aes(label = paste0(round(prop*100), "%")),position = position_fill(),
             show.legend = F) + 
  guides(fill = guide_legend("דירוג")) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) + 
  xlab(paste0("")) + 
  ylab(paste0("\u202B","שיעור המשיבים %")) + 
  ggtitle(paste0("\u202B", "עמדות בנוגע לתובענות ייצוגיות")) + 
  theme(plot.title = element_text(hjust = 1), 
        panel.grid = element_line(color = "gray75"),
        axis.text.x = element_text(size = 12),
        strip.text = element_text(size = 13),
        panel.background = element_rect(fill = NA),
        panel.border = element_rect(fill = NA, color = "gray75")) + 
  scale_fill_brewer(type = "div", palette = "RdYlGn") + 
  labs(caption = "n=180-198")

# ggsave("figures/likert_scale_recoded_all_chart.png", likert_scale_recoded_all_chart, width = 30, height = 10, units = "cm")

```

Now, to do the same but just split between defendent lawyers and prosecuting lawyers

```{r positions split}
likert_scale_recoded_all_split <- likert_scale_recoded %>% 
  group_by(item, q18_representation) %>% 
  prop(ranking) %>% 
  mutate(ranking_factor = 
           recode_factor(ranking,
                         `1` = "כלל לא",
                         `2` = "במידה מועטה",
                         `3` = "במידה בינונית",
                         `4` = "במידה רבה",
                         `5` = "במידה רבה מאוד")) %>% 
  filter(q18_representation %in% c("prosecutors", "defendents")) %>%
  ungroup() %>% 
  mutate(q18_representation = recode(q18_representation,
                                     prosecutors = "מייצגים צד תובע",
                                     defendents = "מייצגים צד נתבע")) %>% 
  
  ungroup() %>% 
  mutate(item = factor(item, levels = sort_order$item))

positions_split <- ggplot(likert_scale_recoded_all_split, aes(x = item, y = prop, fill = factor(ranking, levels = 1:5))) +
  geom_bar(stat = "identity", position = "fill", color = "black") +
  geom_label(aes(label = paste0(round(prop*100), "%")),position = position_fill(),
             show.legend = F) +
  guides(fill = guide_legend("דירוג")) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) + 
  xlab(paste0("")) + 
  ylab(paste0("\u202B","שיעור המשיבים %")) + 
  ggtitle(paste0("\u202B", "עמדות בנוגע לתובענות ייצוגיות")) + 
  theme(plot.title = element_text(hjust = 1), 
        panel.grid = element_line(color = "gray75"),
        axis.text.x = element_text(size = 12, angle = 90),
        strip.text = element_text(size = 13),
        panel.background = element_rect(fill = NA),
        panel.border = element_rect(fill = NA, color = "gray75")) + 
  scale_fill_brewer(type = "div", palette = "RdYlGn") + 
  labs(caption = "n=53-63") + 
  facet_wrap(~q18_representation)

# ggsave("figures/positions_split.png", positions_split, width = 30, height = 10, units = "cm")

```

And now the same only instead of comparing distributions, let's compare averages - simpler to visualize.

```{r positions split averages}
likert_scale_averages <- likert_scale_recoded_all_split %>% 
  group_by(q18_representation, item) %>% 
  summarize(avg = sum(prop*ranking)) %>% 
  ungroup() %>% 
  mutate(q18_representation = recode(q18_representation,
                                     prosecutors = "מייצגים צד תובע",
                                     defendents = "מייצגים צד נתבע"))
likert_scale_averages_chart <- ggplot(likert_scale_averages,
       aes(x = item, y = avg, fill = q18_representation)) +
  geom_col(position = "dodge", color = "black", width = 0.5) +
  xlab(paste0("")) + 
  ylab(paste0("\u202B","ממוצע 1-5")) + 
  geom_label(aes(label = round(avg,2)), position = position_dodge(width = 1), size = 3.5, show.legend = F) +
  ggtitle(paste0("\u202B", "עמדות בנוגע לתובענות ייצוגיות - השוואה בין תובעים למייצגי נתבעים")) + 
  guides(fill = guide_legend("", title.position = "top", title.hjust = 1)) +
  theme(plot.title = element_text(hjust = 1), legend.position = "bottom",
        panel.grid = element_line(color = "gray75"),
        axis.text.y = element_text(size = 12),
        axis.text.x = element_text(size = 13),
        panel.background = element_rect(fill = NA),
        panel.border = element_rect(fill = NA, color = "gray75")) + 
  labs(caption = "n=53-63") + 
  coord_cartesian(ylim = c(1,5))
   
# ggsave("figures/likert_scale_averages_chart.png", likert_scale_averages_chart, width = 30, height = 12, units = "cm") 

```